A Pilot Multicenter Cluster Randomized Trial to Compare The Effect of Trauma Life Support Training Programs on Patient and Provider Outcomes

### 2022-06-09 pilot-publication/manuscript.Rmd
Add IEC registration number for Cooper
Add ethical approval number for LTMGH to manuscrtipt
Add protocol publication citation

## Ethics and Dissemination
We were granted research ethics approval from each participating
hospital. The approval numbers were IEC(II)/OUT/134/2022 for King
Edward Memorial Seth G. S. Medical College and K.E.M. Hospital,
Mumbai; XXX for Lokmanya Tilak Municipal Medical College and General
Hospital, Mumbai; XXX for HBT Medical College And Dr. R N Cooper
Municipal General Hospital, Mumbai; CREC/2022/FEB/1(ii) for Medica
Superspecialty Hospital, Kolkata; Medical College Kolkata, Kolkata;
NRSmC/IEC/93/2021 for Sir Nil Ratan Sircar Medical College & Hospital,
Kolkata; XXX for Postgraduate Institute of Medical Education & Research,
Chandigarh.

The protocol was published in BMJ Open [ADD CITATION] and was
registered with Clinical Trials Registry - India (reg. no XXX) and
ClinicalTrials.gov (reg. no XXX). Amendments to the protocol after
publication were determined by the core research group and updated on
Clinical Trials Registry - India and ClinicalTrials.gov. Substantial
amendments, such as modifications to the eligibility criteria or
outcomes will also be resubmitted to the journal. Declaration of
interest will be submitted from all participating researchers both in
the core team and at each site.

>>>>

## Ethics and Dissemination
We were granted research ethics approval from each participating
hospital. The approval numbers were IEC(II)/OUT/134/2022 for King
Edward Memorial Seth G. S. Medical College and K.E.M. Hospital,
Mumbai; IEC/214/22 for Lokmanya Tilak Municipal Medical College and
General Hospital, Mumbai; HBTMC/266/SURGERY for HBT Medical College
And Dr. R N Cooper Municipal General Hospital, Mumbai;
CREC/2022/FEB/1(ii) for Medica Superspecialty Hospital, Kolkata;
Medical College Kolkata, Kolkata; NRSmC/IEC/93/2021 for Sir Nil Ratan
Sircar Medical College & Hospital, Kolkata; XXX for Postgraduate
Institute of Medical Education & Research, Chandigarh.

The protocol was published in BMJ Open [@GerdinWärnberg2022] and was
registered with Clinical Trials Registry - India (reg. no XXX) and
ClinicalTrials.gov (reg. no XXX). Amendments to the protocol after
publication were determined by the core research group and updated on
Clinical Trials Registry - India and ClinicalTrials.gov. Substantial
amendments, such as modifications to the eligibility criteria or
outcomes will also be resubmitted to the journal. Declaration of
interest will be submitted from all participating researchers both in
the core team and at each site.
